\subsection{Key Setup Infrastructure (Work In Progress)}
\label{sec:infrastructure}

The scope of this subsection is to detail how workers can establish secure channels between themselves without trusting \verb|Cape| and without relying on TLS CA infrastructure. Concurrent to our writing, a blogpost appeared on establishing keys between MPC parties over the internet \cite{url-zengo}.

For our linear regression use case there are three organizations: \verb|A|,
\verb|B| and \verb|Cape|.  Each organization owns a set of workers to perform
computations on encrypted data.  In this context, workers are the parties
running the MPC protocol.  On both sides of \verb|A| and \verb|B| there are
two different types of parties (besides the workers): an operator and a data
scientist denoted as \verb|OpA|, \verb|DS-A|, \verb|OpB|, and \verb|DS-B| respectively.  The
operators and data scientists talk to each other across organizations through
a communication service ran by \verb|Cape|.

We now describe the key steps for workers to establish authenticated secret
channels in order for the replicated computations to be done securely:
\begin{enumerate}
  \item \verb|OpA| generates a signature key pair $\VK_A, \SK_A$ using Libsodium's \verb|crypto_sign_keypair|.
  
  \item The secret key $\SK_A$ is made available to the workers inside organization \verb|A| and a hash of the public verification key $\VK_A$ denoted as $h_A^\OP = \HASH(\VK_A)$ is sent to \verb|B-DS| by the operator \verb|OpA| through \verb|Cape|.
  
  \item Optionally, \verb|B-DS| can check via an authenticated channel (say
  \verb|mail.google.com| or some QR code using Signal app) that the hash $h_A^\OP$ received
  from \verb|Cape| corresponds to the one sent by \verb|OpA|.

  \item On the \verb|B| side the operator \verb|OpB| generates a symmetric key $K_B$
  using \verb|crypto_auth_keygen| in Libsodium.
  Then $K_B$ is broadcasted to all parties on the \verb|B| side (workers and
  data scientist).
  The DS-B fetches $h_A^\OP$ from \verb|Cape| and sends $\tau_{h_A}^\DSB \asn
  \MAC(K_B, h_A^\OP)$ along with $h_A^\DSB \asn h_A^\OP$ to all workers on the B side
  through \verb|Cape| service. This MAC is used by workers on the B side to check
  that the public key setup messages below between workers across organizations are
  forwarded correctly by \verb|Cape|.

  \item On the \verb|A| side all workers $W_A^i$ generate an ephemeral encryption key $\EK_A^i$ and
  its corresponding decryption key $\DK_A^i$ using \verb|crypto_box_keypair|.

  \item For the key-setup between workers, on the \verb|A| side each worker
  sends the encryption key $\EK_A^i$, the verification key $\VK_A$, a
  timestamp \verb|datetime| and a signature $\sigma_i \asn \SIGN(\SK_A,
  \EK_A^i || \verb|datetime|)$ to \verb|Cape|.  These are then forwarded by \verb|Cape|
  to every worker inside organization \verb|B|.  Finally the workers on the
  \verb|B|-side receive the following: $M_\VK, \EK_A^i, \VK_A,
  \verb|datetime|, \sigma^A_i$.  They continue if and only if the following equations
  hold:
  
  \begin{enumerate}
    \item $\HASH(\VK_A) \stackrel{?}{=} h_A^\DSB$.
    \item $\VER(K_B, \tau_{h_A^\DSB}) \stackrel{?}{=} 1$. This ensures that the workers
    received the correct $\HASH(\VK_A)$ sent by \verb|B-DS| through \verb|Cape|.
    \item $\VER(\VK_A, \sigma^i_A) \stackrel{?}{=} 1$
    using the $\VK_A$ received from the worker through \verb|Cape|.
    \item If all checks pass then keep $\EK_A^i$ as the public key for worker $W_A^i$.
    Note that \verb|datetime| is used to prevent replay attacks, this way the workers
    register the other PKs iff \verb|datetime| is within some specific time frame.
  \end{enumerate}

  \item Repeat this for parties on the $B$ side (see Figure~\ref{fig:b-flow}).
\end{enumerate}

After all workers agree on the public key setup infrastructure
using the description above, they continue by calling \verb|crypto_box_easy|
which launches the Curve25519 key exchange. The workers communicate further using a
symmetric key as described in the first section. For more details on the Libsodium API
the reader can refer to Figure~\ref{fig:worker-flow}. Note that communication
between workers happens through an entity called \verb|Broker|, which is
simply forwarding messages between workers. Since \verb|crypto_box_easy| authenticates 
the ciphertexts, they are immune to replay attacks.

% Expiration date for signatures

\input{key-flow/workers-flow}

