\subsection{Sharing data}

In Figure~\ref{fig:replicated-share} we show how a party $D$ can translate a
private tensor $\vx$ (known only to $D$) into a replicated tensor.
Here we distinguish two cases: a) when $D$ is amongst the parties on the replicated placement
i.e. $D \in \{P_1, P_2, P_3\}$ and b) when $D$ is an external party, not in the replicated set.

In the first case the parties use a similar mechanism as in the
$\mathsf{ZeroShare}$ to produce a set of replicated shared seeds. Wlog., consider $D=P_i$,
then $P_i$ sends to $P_{i-1}$ the shape of $\vx$ in order for $P_{i-1}$ to derive a correct
sized random tensor using the shared seed. Then the inputting party
$P_i$ masks the private tensor with a random value $\vx - \vx_i^i$ and sends it
to $P_{i+1}$.

Correctness can be seen from the fact that at the end of the protocol all
$\vx_1^j + \vx_2^j + \vx_3^{j+1} = \vx$ for all $j \in [1,3]$. For example, when
$j = 1$ we have the following: $$\vx_1^1 + \vx_2^1 + \vx_3^2 = \mathbf{0} +
\vx_2^1 + (\vx - \vx_2^2) = \vx $$ due to $\vx_2^1 = \vx_2^2$ since they were
sampled from identical seeds. Security follows from~\cite{CCS:ABFLNO16}
or~\cite{CCS:MohRin18}.


In the second case $D$ is an external party sharing their input. Two of the
parties $(P_1, P_2)$ produce the randomness used to mask $\vx$ in $\vx_3 \asn
\vx - \vx_1 - \vx_2$ such that any two parties can reconstruct the secret
$\share{\vx}$ afterwards. Correctness can be seen as in the first case since all
$\vx_1^j + \vx_2^j + \vx_3^{j+1} = \vx$ for all $j \in [1,3]$. For example, when
$j = 1$ we have: $$ \vx_1^1 + \vx_2^1 + \vx_3^2 = \vx_1 + \vx_2 + (\vx - \vx_1 -
\vx_2) = \vx.$$ The security argument differs slightly then the first case since
$D$ sends $\vx - \vx_1 - \vx_2$ to $P_2$ and $P_3$. Since $\vx_1$ and $\vx_2$ are joint
randomness produced by $P_1$ and $P_2$ then any two parties (no less) can reconstruct the
secret.

\input{protocols/share-input}
