\subsection{Comparison}

%In order to compute the MAPE (mean absolute percentage error) metric which boils down to compute the absolute value of a secret $\share{|\vx|}$. Since our primitives work with ring arithmetic one of its most efficient evaluation of the absolute value is $\share{|\vx|} = \share{\vx} \cdot \share{\vx > 0}$.

The problem of computing secure comparisons translates directly into computing a sharing of the most significant bit $\share{\mathsf{msb}(\vx)}$.
In the 3PC semi-honest model there are few approaches to this:
\begin{enumerate}
  \item ABY3 \cite{CCS:MohRin18}. Each party locally
   bit-decomposes their shares over $\Z_{2^k}$ and then reconstruct the secret
   modulo $\Z_{2^k}$ using shares from $\Z^k_2$ and a binary adder. Once a
   boolean sharing of the MSB is computed using the binary adder this is
   converted to a ring sharing in $\Z_{2^k}$.  The share conversion was
   originally done using a three-party OT protocol.  Later, in MP-SPDZ
   \cite{CCS:Keller20} the boolean to ring secret share conversion was achieved
   with a daBit.

  \item SecureNN \cite{PoPETS:WagGupCha19}.
   Similar to ABY3 with the difference that it uses arithmetic modulo
   small fields but avoids ring-to-boolean conversion.

  \item Extended daBits \cite{C:EGKRS20}. The 3PC case has roughly the same cost as ABY3.
\end{enumerate}

In $\mathsf{moose}$ we use the MSB extraction protocol from ABY3 with a Kogge-Stone binary adder and
minor optimizations for tensor operations. We avoid the special three-party OT
that ABY3 as well as edaBits preprocessing by introducing our custom
protocol \textsf{B2A} for binary to ring share conversion in
Figure~\ref{fig:b2a-protocol}.  The MSB protocol can be found in
Figure~\ref{fig:msb-protocol} where $\overline{\cdot}$ is used to denote a
vector with $k$ elements indexed using $\overline{\cdot}[i]$ for $i \in [k]$.


\input{protocols/msb}

\subsubsection{New boolean to ring sharing protocol}

When the inputs are tensors we can perform the share conversion $\share{\cdot}_2
\mapsto \share{\cdot}_{2^k}$ ($\mathsf{B2A}$ function)
more efficient by making use of the fact that all parties
follow the protocol specifications. The starting point is using a similar idea
from daBit/edaBit \cite{INDOCRYPT:RotWoo19,C:EGKRS20}
line of work with the twist that $P_3$ generates the preprocessing
material.

The protocol works as follows: $P_3$ acts as a trusted third party and generates
a random daBit $(\share{\vb}_2,
\share{\vb}_{2^k})$ locally and shares it to $P_1$ and $P_2$. Note that $P_3$
uses the seed derivation to to minimize the communication between $P_3$ and the
rest of the parties when sharing the random daBit.

Next, $P_1$ and $P_2$ run a two-party protocol to convert $\share{\vx}_2$ to
$\share{\vx}_{2^k}$ by computing the boolean XOR $\share{\vc}_2 \asn
\share{\vx}_2 \oplus \share{\vb}_2$.
Then the two parties $P_1$ and $P_2$ reveal $\share{\vc}_2$
to the random daBit with an XOR in the arithmetic domain
$\vx_{2^k} = \vc + \vb_{2^k} - 2 \cdot \vc \cdot \vb_{2^k}$.
This leaks no information $\vb$ mask uniformly random the input $\vx$.
Finally they securely convert back the additive sharing of $\vx_{2^k}$
denoted as $\share{\vx}^\mathsf{adt}_{2^k}$ to a replicated sharing
$\share{\vx}^\mathsf{rep}_{2^k}$ using $\mathsf{AdtToRep}$ protocol. We fully
describe this share conversion protocol in Figure~\ref{fig:b2a-protocol}.


\input{protocols/b2a}
\input{protocols/dabit}
% \input{protocols/2-out-of-2.tex}
\input{protocols/abs}